---
title: "Combine counts results"
author: "Jia Nie"
date: "11/3/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.
knitr::opts_chunk$set(echo = TRUE)
```

install packages
```{r package, include=FALSE}
packageList <- c("rio", "dplyr", "tibble")
for (package in packageList) {
  if(!require(package, character.only = TRUE)){
    install.packages(package); require(package, character.only = TRUE); }
}
```

# STARR
```{r}
Disk <- c("/media/jianie/Extreme SSD1/") 
# Disk <- c("D:/")
file.folder <- c("08_STARR Patient from Redcap")
basic.file <- "STARR-AllLabTest_DATA_2023-01-24_1405.csv"

Disk2 <- c("/media/jianie/DATA/") 
# Disk2 <- c("C:/Users/niej/Documents/")
file.folder2 <- c("UTHSC_cellranger_codes_files/RedCap_SubjectsInfo")
basic.file2 <- "STARR-BaselineCharacterist_DATA_Final2.xlsx"


file.folder3 <- c("UTHSC_cellranger_codes_files/ExperimentSummaryFiles")
basic.file3 <- "Form 3_cellranger_counts_summary.xlsx"


file.folder4 <- c("UTHSC_cellranger_codes_files/AggrFiles")
basic.file4 <- "STARR.sn.aggr.info.rds"

#Project.folder <- c("2022-08-15 SGLT2 STARR Plasma measurement")
```

# STARR
# basic file from redcap 1: download from online --------------------------------------------------
```{r}
STARR.samples.basic <- rio::import(paste0(Disk, file.folder, "/", basic.file)) %>% 
  mutate(record_id = replace(record_id, record_id == "STRA00100", "STRA0100"),
         record_id = replace(record_id, record_id == "STRA00101", "STRA0101"),
         record_id = toupper(record_id)) %>% 
  arrange(record_id) %>% 
  as.data.frame() %>% 
  rename_with(make.names) %>% 
  rename(Age = `age`, 
         `Height_inches` =  height, 
         `Weight_pounds` = weight, 
         BMI = bmi, 
         Glucose = glucose, 
         `A1c_Value`= hemoglobin_a1c)%>%  
  mutate(Age_Group = ifelse(Age >= 65, "Older", ifelse(Age <65 & Age >= 45, "Middle", "Young")),
         Gender = ifelse(sex == 1, "Female", "Male"),
         Status = ifelse(BMI >= 30, "Obese",
                         ifelse(BMI >= 25 & BMI <30, "Overweight",
                                ifelse(BMI >= 18.5 & BMI <25, "Lean", "NA")))
  )
# dbc4_diabetes
# 0	I DON'T HAVE THIS CONDITION 0
# 1	NOT AT ALL 1
# 2	2: diabetes
# 3	3
# 4	4
# 5	A LOT 5

# dbc12_overwt
# 0	I DON'T HAVE THIS CONDITION 0
# 1	NOT AT ALL 1
# 2	2
# 3	3
# 4	4
# 5	A LOT 5
colnames(STARR.samples.basic)
```


# basic file from redcap 2: personal record --------------------------------------------------
```{r}
STARR.samples.basic1 <- rio::import(paste0(Disk2, file.folder2, "/", basic.file2)) 
colnames(STARR.samples.basic1)
# # sapply(sglt2.samples.basic, class)
intersect(colnames(STARR.samples.basic), colnames(STARR.samples.basic1))

# merge files
STARR.samples <- STARR.samples.basic %>% 
  full_join(STARR.samples.basic1, 
            by = intersect(colnames(STARR.samples.basic), colnames(STARR.samples.basic1))) %>% 
  dplyr::rename(sample_id = id) 
colnames(STARR.samples)

```


# file from sequencing: generate from counts excel file --------------------------------------------------
```{r}
samples.basic3 <- rio::import(paste0(Disk2, file.folder3, "/", basic.file3)) %>%
  dplyr::rename(Status.counts = Status)
colnames(samples.basic3)
intersect(colnames(STARR.samples), colnames(samples.basic3))

# merge files
STARR.samples <- STARR.samples %>% 
  full_join(samples.basic3 %>% 
              dplyr::filter(Project == "STARR"), 
            by = intersect(colnames(STARR.samples), colnames(samples.basic3)))
colnames(STARR.samples)
```

# file from aggregation: generate from aggregation --------------------------------------------------
```{r}
Aggreg <- readRDS(file = paste0(Disk2, file.folder4, "/", basic.file4)) %>% 
  rename(Status.counts = Status) 
Aggreg$Aggr.Number <- paste0("Sample", stringr::str_pad(Aggreg$Agg.List, 2, pad = "0"))
Aggreg$Aggr.Sample <- paste0("STARR")
intersect(colnames(STARR.samples), colnames(Aggreg))

# merge files
STARR.samples <- STARR.samples %>% 
  full_join(Aggreg, 
            by = intersect(colnames(STARR.samples), colnames(Aggreg)))
colnames(STARR.samples)
```


```{r}
# final covert columns
STARR.samples.basic$BMI <- as.numeric(STARR.samples.basic$BMI)
STARR.samples.basic$dbc12_overwt <- as.character(STARR.samples.basic$dbc12_overwt)
STARR.samples.basic$dbc4_diabetes <- as.character(STARR.samples.basic$dbc4_diabetes)

# save
saveRDS(STARR.samples.basic, file = paste0(Disk2, file.folder2, "STARR.all.subject.info.rds"))
```

## STARR_All single nuclei samples:50,000
```{r}
df <- STARR.samples %>% 
  dplyr::filter( Use == "Yes" & Agg == "Yes")
table(df$SingleNuclei, df$Agg)
table(df$Use, df$Agg)
table(df$Age_Group) 
table(df$dbc4_diabetes)
xlsx::write.xlsx(df, file = paste0(Disk2, file.folder2, "STARR.sn.all.subject.info.xlsx"),
                  sheetName = "STARR", row.names=FALSE)
saveRDS(df, file = paste0(Disk2, file.folder2, "STARR.sn.all.subject.info.rds"))
```


## STARR_single nuclei and sequencing ready samples
```{r}
STARR.agg <- readRDS(file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/AggrFiles/STARR.sn.aggr.info.rds") %>% rename(Status.counts = Status)
intersect(colnames(starr.samples.all), colnames(STARR.agg))
starr.sn <- STARR.agg %>% left_join(starr.samples.all, by = c("sample_id" = "id")) %>% arrange(Agg.List) # %>% select(all_of(starr.samples.cols)) 
table(starr.sn$Age_Group) 
table(starr.sn$dbc12_overwt)
xlsx::write.xlsx(starr.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.aggr.combine.info.xlsx", sheetName = "STARR", row.names=FALSE)
saveRDS(starr.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.aggr.combine.info.rds")
```


```{r}
c("id", "SingleNuclei", "Record ID: 766-", "Age at Consent", "Age (years)", "Group Assignment:",
  "Gender" , "Event Name" , "Height (inches)" , "Weight (pounds)",  "BMI", "Glucose" , "A1c Value", 
  "dbc12_overwt", 
  "Blood Pressure Systolic", "Blood Pressure Diastolic", 
  "Cholesterol, Total" , "triglycerides" , "HDL", "LDL" )
  
  select(!one_of(c("Complete?", "Date:"))) %>%%>%
  rename(dbc12_overwt = Diabetes) %>%
  as.data.frame() %>%
  rename_with(make.names) %>%
  select(one_of(c("id", "SingleNuclei", "AdiposeTissue", "Plasma", "Finished",
                  "Record.ID..766.", "Event.Name_Orig", "Event.Name"))
  )
  select(!one_of(c("Complete?", "Date:"))) %>% 
  rename(dbc12_overwt = Diabetes, 
         X.30.Glucose.1 = `-30 Glucose`, 
         X.30.Insulin.1 = `-30 Insulin`) %>% 
  as.data.frame() %>% 
  rename_with(make.names)
colnames(STARR.samples.basic)

```



```{r}
# Disk <- c("/media/jianie/Extreme SSD1/") 
Disk <- c("D:/")
# Disk3 <- c("C:/Users/niej/Desktop/")
Disk3 <- c("D:/")
Project.folder <- c("2022-08-15 SGLT2 STARR Plasma measurement")
file.folder <- c("07_SGLT2 from redcap")
```

# SGLT2
```{r}
# basic file from redcap 1 --------------------------------------------------
# Disk2 <- c("/media/jianie/DATA/") 
Disk2 <- c("C:/Users/niej/Documents/")
basic.file <- "SGLT2iAndAging-Test1Csh_DATA_LABELS_Final.csv"
sglt2.samples.basic1 <- rio::import(paste0(Disk2,
                                           "UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/",
                                           basic.file)) %>%
  select(!one_of(c("Complete?", "Date:"))) %>%
  rename(dbc12_overwt = Diabetes) %>%
  as.data.frame() %>%
  rename_with(make.names) %>%
  select(one_of(c("id", "SingleNuclei", "AdiposeTissue", "Plasma", "Finished",
                  "Record.ID..766.", "Event.Name_Orig", "Event.Name"))
  )
colnames(sglt2.samples.basic1)
# # sapply(sglt2.samples.basic, class)
c("id", "SingleNuclei", "Record ID: 766-", "Age at Consent", "Age (years)", "Group Assignment:",
  "Gender" , "Event Name" , "Height (inches)" , "Weight (pounds)",  "BMI", "Glucose" , "A1c Value", 
  "dbc12_overwt", 
  "Blood Pressure Systolic", "Blood Pressure Diastolic", 
  "Cholesterol, Total" , "triglycerides" , "HDL", "LDL" )


# basic file from redcap 2 --------------------------------------------------
# Disk2 <- c("/media/jianie/DATA/") 
basic.file <- "SGLT2iAndAging-AllLabTest_DATA_LABELS_2022-09-29_1706.csv"
sglt2.samples.basic <- rio::import(paste0(Disk3, file.folder, "/",
                                          basic.file)) %>% 
  select(!one_of(c("Complete?", "Date:"))) %>% 
  rename(dbc12_overwt = Diabetes, 
         X.30.Glucose.1 = `-30 Glucose`, 
         X.30.Insulin.1 = `-30 Insulin`) %>% 
  as.data.frame() %>% 
  rename_with(make.names)
colnames(sglt2.samples.basic)
intersect(colnames(sglt2.samples.basic), colnames(sglt2.samples.basic1))
# Diabetes
# yesno
# 1	Yes
# 0	No


sglt2.samples.basic <- sglt2.samples.basic %>% 
  full_join(sglt2.samples.basic1, 
            by = intersect(colnames(sglt2.samples.basic), colnames(sglt2.samples.basic1)))

# combine -------------------------------------------------------------------
merge.cols <- intersect(colnames(data.mean), colnames(sglt2.samples.basic))
sglt2.samples.all <- sglt2.samples.basic %>% 
  left_join(data.mean, by = merge.cols) %>% 
  rename_with(make.names)
colnames(sglt2.samples.all)

```



# Generate sequencing form
```{r}
<<<<<<< HEAD
select.cols <- c("Counts_List","SQ_List","Sequencing_Date", "Lane","sample_id","sample_id_ori","Agg","Status.counts","Project","AnalysisDate","Done","Sequencing_Type" )
select.starrs <- aggr %>% dplyr::filter(Project == "STARR" & Agg == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
select.starrs2 <- aggr %>% dplyr::filter(Project == "STARR" & Agg_43 == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
select.sglt2 <- aggr %>% dplyr::filter(Project == "SGLT2" & Agg == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
=======
select.sequencing.cols <- c("Counts_List","SQ_List","Sequencing_Date", "Lane","sample_id","sample_id_ori","Agg","Status.counts","Project","AnalysisDate","Done","Sequencing_Type" )
>>>>>>> 2772705fed8e1d608581d148bf93f27ec5bc56b4

# STARR
select.starrs <- samples.basic3 %>% dplyr::filter(Project == "STARR" & Agg == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
sequencing.info <- samples.basic3 %>% 
  dplyr::filter(Project == "STARR" &  
                  Status.counts == "Original" & 
                  ! Agg %in% c("Hf test", "FZ test", "Bar test") &
                  sample_id %in% select.starrs) %>% 
  arrange(sample_id) %>% 
  select(all_of(select.sequencing.cols))
xlsx::write.xlsx(sequencing.info, file = paste0(Disk2, file.folder2, "/", "Sequencing Files_STARR.xlsx"), row.names=FALSE)

sequencing.info <- aggr %>% dplyr::filter(Project == "STARR" &  Status.counts == "Original" & 
                                     ! Agg %in% c("Hf test", "FZ test", "Bar test") &
                                     sample_id %in% select.starrs2) %>% arrange(sample_id) %>% select(all_of(select.cols))
xlsx::write.xlsx(sequencing.info, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/Sequencing Files_STARR_43.xlsx", row.names=FALSE)


# SGLT2
select.sglt2 <- samples.basic3 %>% dplyr::filter(Project == "SGLT2" & Agg == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
sequencing.info <- samples.basic3 %>% 
  dplyr::filter(Project == "SGLT2" &  
                  Status.counts == "Original" & 
                                     ! Agg %in% c("Hf test", "FZ test", "Bar test") &
                                     sample_id %in% select.sglt2) %>% 
  arrange(sample_id) %>% 
  select(all_of(select.sequencing.cols))
xlsx::write.xlsx(sequencing.info, file = paste0(Disk2, file.folder2, "/", "Sequencing Files_SGLT2.xlsx"), row.names=FALSE)

# STARR & SGLT2
select.starrs <- samples.basic3 %>% dplyr::filter(Project == "STARR" & Agg_43 == "Yes") %>% arrange(sample_id) %>% pull(sample_id)
select.sglt2 <- samples.basic3 %>% dplyr::filter(Project == "SGLT2" & Agg_43 == "Yes") %>% arrange(sample_id) %>% pull(sample_id)

sequencing.info <- samples.basic3 %>% 
  dplyr::filter(Project %in% c("STARR", "SGLT2") &  
                  Status.counts == "Original" & 
                                     ! Agg %in% c("Hf test", "FZ test", "Bar test") &
<<<<<<< HEAD
                                     sample_id %in% c(select.starrs2, select.sglt2)) %>% arrange(sample_id) %>% select(all_of(select.cols))
xlsx::write.xlsx(sequencing.info, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/Sequencing Files_combine.xlsx", row.names=FALSE)
=======
                                     sample_id %in% c(select.starrs, select.sglt2)) %>% 
  arrange(sample_id) %>% 
  select(all_of(select.sequencing.cols))
xlsx::write.xlsx(sequencing.info, file = paste0(Disk2, file.folder2, "/", "Sequencing Files_SGLT2_STARR.xlsx"), row.names=FALSE)
>>>>>>> 2772705fed8e1d608581d148bf93f27ec5bc56b4
```


```{r}
rm(select.sequencing.cols, select.starrs, select.sglt2, sequencing.info)

```





# STARR 
```{r}
starr.samples.all <- rio::import("/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR-BaselineCharacterist_DATA_Final.xlsx") 
colnames(starr.samples.all) 
starr.samples.cols <- c("id", "SingleNuclei", "record_id", "recruited_from", 
                          "age" , "sex", "weight" , "height", "bmi", "glucose" ,"fasting",  "hemoglobin_a1c", "dbc12_overwt",
                          "systolic" , "diastolic" , 
                          "cholesterol" , "triglycerides" , "hdl", "ldl" )
starr.samples.all <- starr.samples.all %>%  arrange(id) %>% 
  rename(Age = `age`, `Height (inches)` =  height, `Weight (pounds)` = weight, BMI = bmi, Glucose = glucose, `A1c Value`= hemoglobin_a1c)%>%  
  mutate(Age_Group = ifelse(Age >= 65, "Older", ifelse(Age <65 & Age >= 45, "Middle", "Young")),
         Gender = ifelse(sex == 1, "Female", "Male"),
         Status = ifelse(BMI >= 30, "Obese",
                         ifelse(BMI >= 25 & BMI <30, "Overweight",
                                ifelse(BMI >= 18.5 & BMI <25, "Lean", "NA")))
  )

starr.samples.cols <- c("id", "SingleNuclei", "record_id", "recruited_from", 
                        "Gender", 
                        "Age" ,"Age_Group",
                        "Height (inches)" , "Weight (pounds)", "BMI", "Status",
                        "Glucose" ,  "A1c Value", "fasting", "dbc4_diabetes")

starr.samples.all$BMI <- as.numeric(starr.samples.all$BMI)
starr.samples.all$dbc12_overwt <- as.character(starr.samples.all$dbc12_overwt)

saveRDS(starr.samples.all, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.all.subject.info.rds")
```

## STARR_All single nuclei samples
```{r}
starr.sn.all <- starr.samples.all %>% dplyr::filter( SingleNuclei == "Yes") %>% arrange(id) %>% select(all_of(starr.samples.cols)) 
table(starr.sn.all$Age_Group) 
table(starr.sn.all$dbc4_diabetes)
xlsx::write.xlsx(starr.sn.all, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.all.subject.info.xlsx", sheetName = "STARR", row.names=FALSE)
saveRDS(starr.sn.all, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.all.subject.info.rds")
```

## STARR_single nuclei and sequencing ready samples
```{r}
STARR.agg <- readRDS(file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/AggrFiles/STARR.sn.aggr.info.rds") %>% rename(Status.counts = Status)
intersect(colnames(starr.samples.all), colnames(STARR.agg))
starr.sn <- STARR.agg %>% left_join(starr.samples.all, by = c("sample_id" = "id")) %>% arrange(Agg.List) # %>% select(all_of(starr.samples.cols)) 
table(starr.sn$Age_Group) 
table(starr.sn$dbc12_overwt)
xlsx::write.xlsx(starr.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.aggr.combine.info.xlsx", sheetName = "STARR", row.names=FALSE)
saveRDS(starr.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR.sn.aggr.combine.info.rds")
```











# SGLT2_All single nuclei samples
```{r}
sglt2.samples.all <- rio::import("/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/SGLT2iAndAging-Test1Csh_DATA_LABELS_Final.xlsx") %>% rename(dbc12_overwt = Diabetes)
colnames(sglt2.samples.all)
c("id", "SingleNuclei", "Record ID: 766-", "Age at Consent", "Age (years)", "Group Assignment:",
  "Gender" , "Event Name" , "Height (inches)" , "Weight (pounds)",  "BMI", "Glucose" , "A1c Value", "dbc12_overwt",
  "Blood Pressure Systolic", "Blood Pressure Diastolic", 
  "Cholesterol, Total" , "triglycerides" , "HDL", "LDL" )

# adjust columns
sglt2.samples.all <- sglt2.samples.all %>% 
  rename( Age = `Age at Consent` 
  )%>% 
  mutate(Age_Group = ifelse(Age >= 65, "Older", ifelse(Age <65 & Age >= 45, "Middle", "Young")),
         Status = ifelse(BMI >= 30, "Obese",
                         ifelse(BMI >= 25 & BMI <30, "Overweight",
                                ifelse(BMI >= 18.5 & BMI <25, "Lean", "NA"))),
         patient_id = paste0("766", `Record ID: 766-`),
         Group = ifelse(`Group Assignment:` == "Drug - dapagliflozin", "D",
                        ifelse(`Group Assignment:` == "Nutritional counseling", "C", "NA"))
  )
select.sglt2 <- sglt2.samples.all %>% dplyr::filter(SingleNuclei == "Yes") %>% arrange(id) %>% pull(patient_id) %>% unique()

# adjust and combine parameters between V1, V5, V11.
sglt2.V1.cols <- c("id", "Record ID: 766-", "patient_id", "Event Name" , 
                   "Race","Gender",
                   "Age", "Age_Group",
                   #"Height (inches)" , "Weight (pounds)",  "BMI", "Status",
                   "Glucose" , "A1c Value", "dbc12_overwt")
sglt2.sn.V1 <- sglt2.samples.all %>% dplyr::filter(`Event Name` == "Visit 1") %>% arrange(id) %>% select(all_of(sglt2.V1.cols)) %>% 
  rename( id.V1 = id, `Event Name_V1` = `Event Name`
  )

sglt2.V5.cols <- c("id", "Record ID: 766-","patient_id", "Event Name" , 
                   "SingleNuclei", "Group Assignment:", "Group",
                    "Height (inches)" , "Weight (pounds)",  "BMI", "Status"
                   )
sglt2.sn.V5 <- sglt2.samples.all %>% dplyr::filter(`Event Name` == "Visit 5",  SingleNuclei == "Yes") %>% arrange(id) %>% select(all_of(sglt2.V5.cols)) 
sglt2.sn.basal <- sglt2.sn.V5 %>% left_join(sglt2.sn.V1, by = c("Record ID: 766-", "patient_id"))

sglt2.V11.cols <- c("id", "Record ID: 766-","patient_id", "Event Name" , 
                   "SingleNuclei", 
                   "Height (inches)" , "Weight (pounds)",  "BMI", "Status",
                   "Glucose" , "A1c Value")
sglt2.sn.V11 <- sglt2.samples.all %>% dplyr::filter(`Event Name` == "Visit 11",  SingleNuclei == "Yes") %>% arrange(id) %>% select(all_of(sglt2.V11.cols)) 
sglt2.sn.V11 <- sglt2.sn.V11 %>% left_join(sglt2.sn.V1 %>% select(!all_of(c("Glucose" , "A1c Value"))) , by = c("Record ID: 766-", "patient_id")) %>%
  left_join(sglt2.sn.V5 %>% select(all_of(c("patient_id" , "Group Assignment:", "Group"))), by = c("patient_id"))

# combine final
sglt2.sn.all <- sglt2.sn.V11 %>% full_join(sglt2.sn.basal, by = intersect(colnames(sglt2.sn.V11),  colnames(sglt2.sn.basal)) ) %>% arrange(patient_id) %>%
  select(!one_of(c("Group Assignment:")))
sglt2.sn.all$BMI <- as.numeric(sglt2.sn.all$BMI)
sglt2.sn.all$dbc12_overwt <- as.character(sglt2.sn.all$dbc12_overwt)

table(sglt2.sn.all$Age_Group) 
table(sglt2.sn.all$dbc12_overwt)

# save result
xlsx::write.xlsx(sglt2.sn.all, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/sglt2.sn.all.subject.info.xlsx", sheetName = "SGLT2", row.names=FALSE)
saveRDS(sglt2.sn.all, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/sglt2.sn.all.subject.info.rds")
```


```{r}
rm(sglt2.sn.V1, sglt2.sn.V5, sglt2.sn.V11, sglt2.sn.basal, sglt2.samples.all)
```

## SGLT2_single nuclei and sequencing ready samples
```{r}
SGLT2.agg <- readRDS(file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/AggrFiles/SGLT2.Final.rds") %>% rename(Status.counts = Status)
library(readr)
# SGLT2.agg <- read_csv("/media/jianie/DATA/UTHSC_cellranger_codes_files/AggrFiles/SGLT2.Final_20.csv") %>% rename(Status.counts = Status)
intersect(colnames(sglt2.sn.all), colnames(SGLT2.agg)) # should be character(0)
SGLT2.sn <- SGLT2.agg %>% left_join(sglt2.sn.all, by = c("sample_id" = "id")) %>% arrange(Agg.List) # %>% select(all_of(starr.samples.cols)) 
table(SGLT2.sn$Age_Group) 
table(SGLT2.sn$dbc12_overwt)
table(SGLT2.sn$`Event Name`)
xlsx::write.xlsx(as.data.frame(SGLT2.sn), file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/SGLT2.sn.aggr.combine.info.xlsx", sheetName = "SGLT2", row.names=FALSE, append = FALSE)
saveRDS(SGLT2.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/SGLT2.sn.aggr.combine.info.rds")
```

```{r}
rm(SGLT2.agg)
```






# STARR_SGLT2_combine single nuclei and sequencing ready samples
```{r}
combine.agg <- readRDS(file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/AggrFiles/STARR.SGLT2.agg.rds") %>% rename(Status.counts = Status) %>% mutate(Agg.List = 1:n())
intersect(colnames(sglt2.sn.all), colnames(combine.agg))
intersect(colnames(starr.samples.all), colnames(combine.agg))
intersect(colnames(starr.samples.all), colnames(sglt2.sn.all ))

sample.all <- starr.samples.all %>% full_join(sglt2.sn.all ,  by = c(intersect(colnames(starr.samples.all), colnames(sglt2.sn.all ))))
combine.sn <- combine.agg %>% left_join(sample.all, by = c("sample_id" = "id")) %>% arrange(Agg.List) 

table(combine.sn$Age_Group) 
table(combine.sn$dbc12_overwt)
xlsx::write.xlsx(combine.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR_SGLT2.sn.aggr.combine.info.xlsx", sheetName = "STARR_SGLT2", row.names=FALSE)
saveRDS(combine.sn, file = "/media/jianie/DATA/UTHSC_cellranger_codes_files/RedCap_SubjectsInfo/STARR_SGLT2.sn.aggr.combine.info.rds")
```

