---
title: "Sample information"
author: "Jia Nie"
date: "11/3/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.
knitr::opts_chunk$set(echo = TRUE)
```

install packages
```{r package, include=FALSE}
packageList <- c("rio", "dplyr", "tibble")
for (package in packageList) {
  if(!require(package, character.only = TRUE)){
    install.packages(package); require(package, character.only = TRUE); }
}
```

# STARR
## add files -------------------
```{r}
Disk1 <- c("/media/jianie/Extreme SSD/") 
# Disk1 <- c("D:/")
file.folder1 <- c("08_STARR Patient from Redcap")# download from online
basic.file1 <- "STARR-AllLabTest_DATA_2023-01-24_1405.csv"

Disk2 <- c("/media/jianie/DATA/") 
# Disk2 <- c("C:/Users/niej/Documents/")
file.folder2 <- c("UTHSC_cellranger_codes_files/RedCap_SubjectsInfo") # personal record 
basic.file2 <- "STARR-BaselineCharacterist_DATA_Final2.xlsx"

Disk3 <- c("/media/jianie/Extreme SSD/") 
# Disk3 <- c("D:/")
file.folder3 <- c("08_STARR Patient from Redcap")# download from online
basic.file3 <- "STARR-Diabetes_DATA_2023-05-17_1058_2.xlsx"

# Disk3 <- c("/media/jianie/DATA/") 
# # Disk3 <- c("C:/Users/niej/Documents/")
# file.folder3 <- c("UTHSC_cellranger_codes_files/ExperimentSummaryFiles") # generate from counts excel file
# basic.file3 <- "Form 3_cellranger_counts_summary.xlsx"

# Disk4 <- c("/media/jianie/DATA/") 
# # Disk4 <- c("C:/Users/niej/Documents/") 
# file.folder4 <- c("UTHSC_cellranger_codes_files/AggrFiles") # aggregation
# basic.file4 <- "STARR.sn.aggr.info.rds"


Disk5 <- c("/media/jianie/Extreme SSD/") 
# Disk5 <- c("D:/")
file.folder5 <- c("2022-08-15 SGLT2 STARR Plasma measurement")
basic.file5 <- c("All Results.mean.csv")
```

## basic file from redcap 1: download from online --------------------------------------------------
```{r}
STARR.samples.basic1 <- rio::import(paste0(Disk1, file.folder1, "/", basic.file1)) %>% 
  mutate(record_id = replace(record_id, record_id == "STRA00100", "STRA0100"),
         record_id = replace(record_id, record_id == "STRA00101", "STRA0101"),
         record_id = toupper(record_id)) %>% 
  arrange(record_id) %>% 
  as.data.frame() %>% 
  rename_with(make.names) %>% 
  rename(Age = `age`, 
         `Height_inches` =  height, 
         `Weight_pounds` = weight, 
         # BMI = bmi, 
         Glucose = glucose, 
         A1c_Value= hemoglobin_a1c)%>%  
  mutate(         BMI = 703*Weight_pounds/(Height_inches^2) )%>%
  mutate(Age_Group = ifelse(Age >= 60, "Older", ifelse(Age < 60 & Age >= 45, "Middle", "Young")),
         Gender = ifelse(sex == 1, "Female", "Male"),
         Prediabetes1 = ifelse(A1c_Value >= 5.7 & A1c_Value <= 6.4, "PreD", 
                               ifelse(A1c_Value > 6.4, "Diabetes", "No" )),
         Prediabetes2 = ifelse(Glucose >= 100 & Glucose <= 125, "PreD", 
                               ifelse(Glucose > 125, "Diabetes", "No" )),
         Status = ifelse(BMI >= 30, "Obese",
                         ifelse(BMI >= 25 & BMI <30, "Overweight",
                                ifelse(BMI >= 18.5 & BMI <25, "Lean", 
                                       ifelse(BMI <18.5, "Underweight", "NA"))))
  ) %>%
  mutate(Diabetes = ifelse( dbc4_diabetes == 2 | diabetes_doctor == 1, "Yes", "No"), # 
         Ethnicity = ifelse(ethnicity == 1, "Hispanic or Latino", "NOT Hispanic or Latino")
  ) %>% 
  rename(Blood.Pressure.Systolic = systolic,
         Blood.Pressure.Diastolic = diastolic, 
         White.Blood.Cell...WBC = white_blood_cell,                    
         Red.Blood.Cell...RBC = red_blood_cell,  
         Hemoglobin = hemoglobin,                         
         Hematocrit = hematocrit,                       
         MCV = mcv,                            
         MCH = mch,      
         Platelets  = platelets,          
         Blood.Urea.Nitrogen..BUN. = bun,  
         Creatinine = creatinine,                
         Sodium = sodium,
         Potassium = potassium, 
         Calcium = calcium,                                  
         Protein..Total = protein_total,                         
         Albumin = albumin,              
         Alkaline.Phosphatase = alkaline_phosphatase,
         Bilirubin..Total = total_bilirubin,                    
         AST = ast, 
         ALT = alt,                     
         Cholesterol..Total = cholesterol,                       
         Triglycerides = triglycerides,                               
         HDL = hdl,
         LDL = ldl,                                  
         VLDL = vldl          
         #,  Ethnicity = ethnicity
  )%>%
   mutate(Race = ifelse(race___5 == 1, "White", "No"))

table(STARR.samples.basic1$Age_Group)
table(STARR.samples.basic1$Gender)
sort(unique(STARR.samples.basic1$BMI))
table(STARR.samples.basic1$Status)
table(STARR.samples.basic1$Diabetes)

table(STARR.samples.basic1$dbc4_diabetes); unique(STARR.samples.basic1$dbc4_diabetes)
# dbc4_diabetes
# 0	I DON'T HAVE THIS CONDITION 0
# 1	NOT AT ALL 1
# 2	2: diabetes
# 3	3
# 4	4
# 5	A LOT 5

table(STARR.samples.basic1$diabetes_doctor); unique(STARR.samples.basic1$diabetes_doctor)
# diabetes_doctor
# 1-Yes
# 2-No


table(STARR.samples.basic1$dbc12_overwt)
# dbc12_overwt
# 0	I DON'T HAVE THIS CONDITION 0
# 1	NOT AT ALL 1
# 2	2
# 3	3
# 4	4
# 5	A LOT 5

table(STARR.samples.basic1$race___1)
table(STARR.samples.basic1$race___2)
table(STARR.samples.basic1$race___3)
table(STARR.samples.basic1$race___4)
table(STARR.samples.basic1$race___5)
table(STARR.samples.basic1$race___6)
table(STARR.samples.basic1$race___7)
# 37 [race] 2. What is your race? Please indicate all that apply checkbox
# 1 race___1 American Indian or Alaska Native
# 2 race___2 Asian
# 3 race___3 Black or African American
# 4 race___4 Native Hawaiian or Other Pacific Islander
# 5 race___5 White
# 6 race___6 Some other race or origin
# 7 race___7 DK/REF
table(STARR.samples.basic1$race___5, STARR.samples.basic1$race___1)
table(STARR.samples.basic1$ethnicity)
# 38 [ethnicity] Are you of Hispanic, Latino, or Spanish origin? radio
# 1 Yes
# 2 No

colnames(STARR.samples.basic1)
```


## basic file from redcap 2: personal record --------------------------------------------------
```{r}
STARR.samples.basic2 <- rio::import(paste0(Disk2, file.folder2, "/", basic.file2)) 
colnames(STARR.samples.basic2)
# # sapply(sglt2.samples.basic, class)
intersect(colnames(STARR.samples.basic1), colnames(STARR.samples.basic2))

# merge files
STARR.samples <- STARR.samples.basic1 %>% 
  full_join(STARR.samples.basic2, 
            by = intersect(colnames(STARR.samples.basic1), colnames(STARR.samples.basic2))) %>% 
  dplyr::rename(sample_id = id) 
colnames(STARR.samples)
```

## basic file from redcap 3: download from online --------------------------------------------------
```{r}
STARR.samples.basic3 <- rio::import(paste0(Disk3, file.folder3, "/", basic.file3)) %>% 
  mutate(record_id = replace(record_id, record_id == "STRA00100", "STRA0100"),
         record_id = replace(record_id, record_id == "STRA00101", "STRA0101"),
         record_id = toupper(record_id)) %>% 
  arrange(record_id) %>% 
  as.data.frame() %>% 
  rename_with(make.names) %>% 
  rename(
    Glucose = glucose, 
    A1c_Value= hemoglobin_a1c)%>%  
  mutate(
         Medicine.Status = ifelse(medication_1_name %in% c("****NO MEDICATIONS*****", "***NO MEDICATIONS TO REPORT***",
                                                           "no medication to report", NA), "NoHistory", "YesMedicine"),
         diabetes_doctor = ifelse(diabetes_doctor == "No (SKIP TO CHOLESTEROL) (2)", 2, 
                                  ifelse(diabetes_doctor == "Yes (1)", 1, NA)),
         dbc4_diabetes = ifelse(dbc4_diabetes == "2 (2)", 2, 
                                  ifelse(dbc4_diabetes == "NOT AT ALL 1 (1)", 1, 
                                         ifelse(dbc4_diabetes == "I DON'T HAVE THIS CONDITION 0 (0)", 0, NA)))
  ) %>% 
  rename(
         Creatinine = creatinine,                
  )
table(STARR.samples.basic1$Medicine.Status); unique(STARR.samples.basic3$Medicine.Status)
table(STARR.samples.basic3$medication_1_name); unique(STARR.samples.basic3$medication_1_name)
table(STARR.samples.basic3$diabetes_doctor); unique(STARR.samples.basic3$diabetes_doctor)
table(STARR.samples.basic3$dbc4_diabetes); unique(STARR.samples.basic3$dbc4_diabetes)
colnames(STARR.samples.basic3)

intersect(colnames(STARR.samples), colnames(STARR.samples.basic3))


# merge files
STARR.samples <- STARR.samples %>% 
  full_join(STARR.samples.basic3, 
            by = intersect(colnames(STARR.samples), colnames(STARR.samples.basic3))) 
colnames(STARR.samples)
```


## basic file from sequencing: generate from counts excel file --------------------------------------------------
```{r}
# samples.basic3 <- rio::import(paste0(Disk3, file.folder3, "/", basic.file3)) %>%
#   dplyr::rename(Status.counts = Status)
# colnames(samples.basic3)
# intersect(colnames(STARR.samples), colnames(samples.basic3))
# 
# # merge files
# STARR.samples <- STARR.samples %>% 
#   full_join(samples.basic3 %>%  dplyr::filter(Project == "STARR"), by = intersect(colnames(STARR.samples), colnames(samples.basic3)))
# colnames(STARR.samples)
```

## basic file from aggregation: generate from aggregation --------------------------------------------------
```{r}
# Aggreg <- readRDS(file = paste0(Disk4, file.folder4, "/", basic.file4)) %>%
#   rename(Status.counts = Status)
# Aggreg$Aggr.Number <- paste0("Sample", stringr::str_pad(Aggreg$Agg.List, 2, pad = "0"))
# Aggreg$Aggr.Sample <- paste0("STARR")
# intersect(colnames(STARR.samples), colnames(Aggreg))
# 
# # merge files
# STARR.samples <- STARR.samples %>%
#   full_join(Aggreg,
#             by = intersect(colnames(STARR.samples), colnames(Aggreg)))
# colnames(STARR.samples)
```

## basic file from lab: lab measurements --------------------------------------------------
```{r}
samples.basic5 <- rio::import(file = paste0(Disk5, file.folder5, "/", basic.file5)) # %>%
# rename(sample_id = id)
intersect(colnames(STARR.samples), colnames(samples.basic5))

# merge files
STARR.samples <- STARR.samples %>%
  left_join(samples.basic5,
            by = intersect(colnames(STARR.samples), colnames(samples.basic5)))
colnames(STARR.samples)
```

## combine all ------------------
```{r}
# final covert columns
STARR.samples$BMI <- as.numeric(STARR.samples$BMI)
STARR.samples$dbc12_overwt <- as.character(STARR.samples$dbc12_overwt)
STARR.samples$dbc4_diabetes <- as.character(STARR.samples$dbc4_diabetes)
STARR.samples$diabetes_doctor <- as.character(STARR.samples$diabetes_doctor)
STARR.samples$Albumin <- as.numeric(STARR.samples$Albumin)
STARR.samples$Group <- "Notreatment"
STARR.samples$Pre_Post <- "Notreatment"
# save
saveRDS(STARR.samples, file = paste0(Disk2, file.folder2, "/", "STARR.all.subject.info.rds"))
```


## STARR_All single nuclei samples -------------------
```{r}
# df <- STARR.samples %>% dplyr::filter( Use == "Yes" & Agg == "Yes")
# df <- STARR.samples %>% dplyr::filter( Use == "Yes" & Agg_43 == "Yes")
# table(df$SingleNuclei, df$Agg_43)
# table(df$Use, df$Agg_43)
# table(df$Age_Group) 
# table(df$dbc4_diabetes)
# xlsx::write.xlsx(df, file = paste0(Disk2, file.folder2, "/", "STARR.sn.all.subject.info.xlsx"), sheetName = "STARR", row.names=FALSE)
# saveRDS(df, file = paste0(Disk2, file.folder2, "/", "STARR.sn.all.subject.info.rds"))
```

```{r}
rm(df, samples.basic3, STARR.samples.basic1, STARR.samples.basic2)
```


# SGLT2
## add files -------------
```{r}
Disk1 <- c("/media/jianie/Extreme SSD/") 
# Disk1 <- c("D:/")
file.folder1 <- c("07_SGLT2 from Redcap") # download from online
basic.file1 <- "SGLT2iAndAging-AllLabTest_DATA_LABELS_2022-09-29_1706.csv"
# basic.file1 <- "SGLT2iAndAging-AllLabTest_DATA_LABELS_2023-02-24_0934.csv"
basic.file1.1 <- "SGLT2iAndAging_DATA_LABELS_2023-02-24_0951.csv"

Disk2 <- c("/media/jianie/DATA/") 
# Disk2 <- c("C:/Users/niej/Documents/")
file.folder2 <- c("UTHSC_cellranger_codes_files/RedCap_SubjectsInfo")  # download from online by Allison # 76649_V1, Bilirubin..Total < 0.2, change to 76649_V6, Bilirubin..Total 0.4
basic.file2 <- "SGLT2iAndAging-Test1Csh_DATA_LABELS_Final.csv"


# Disk3 <- c("/media/jianie/DATA/") 
# # Disk3 <- c("C:/Users/niej/Documents/")
# file.folder3 <- c("UTHSC_cellranger_codes_files/ExperimentSummaryFiles") # generate from counts excel file
# basic.file3 <- "Form 3_cellranger_counts_summary.xlsx"


# Disk4 <- c("/media/jianie/DATA/") 
# # Disk4 <- c("C:/Users/niej/Documents/") 
# file.folder4 <- c("UTHSC_cellranger_codes_files/AggrFiles") # aggregation
# basic.file4 <- "STARR.sn.aggr.info.rds"

Disk5 <- c("/media/jianie/Extreme SSD/") 
# Disk5 <- c("D:/")
file.folder5 <- c("2022-08-15 SGLT2 STARR Plasma measurement") # other measurements
basic.file5 <- c("All Results.mean.csv")

```

## basic file from redcap 1  --------------------------------------------------
```{r}
library("tidyr")
sglt2.samples.basic1 <- rio::import(paste0(Disk1, file.folder1, "/", basic.file1)) %>% 
  dplyr::select(!one_of(c("Complete?", "Date:"))) %>% 
  rename(dbc4_diabetes = Diabetes, 
         # `Visit_Num` = `Visit #`,
         X.30.Glucose.1 = `-30 Glucose`,
         X.30.Insulin.1 = `-30 Insulin`
  ) %>% 
  as.data.frame() %>% 
  rename_with(make.names) %>% 
  mutate(Event.Name1 = stringr::str_split_fixed(Event.Name, " ", 2)[, 2] ) %>%
  mutate(Event.Name2 = stringr::str_split_fixed(Event.Name1, " ", 2)[, 1],
         Event.Name3 = ifelse(stringr::str_split_fixed(Event.Name1, " ", 2)[, 2] == "",  "",  ".1week")
  ) %>%
  mutate(patient_id =   paste0("766", stringr::str_pad( Record.ID..766., 2, pad = "0") ),
         # Event = readr::parse_number(as.character(Event.Name), na = c("Logs", "Checklists", "Unscheduled Visit", "Repeat Labs"))
  ) %>%
  # mutate_at(c('Event'), ~replace_na(., ""))  %>% 
  mutate(Event_id =  paste0("V", Event.Name2,  ifelse(Event.Name3 == "", "", Event.Name3) ) # paste0("V", stringr::str_pad(Event, 2, pad = "0") )
  ) %>%
  mutate(Event_id = replace(Event_id, Event_id == "V", "") ) %>%
  mutate(sample_id =  paste0(patient_id, ifelse(Event_id == "", "","_") , Event_id) ) %>%
  left_join(
    rio::import(paste0(Disk1, file.folder1, "/", basic.file1.1)) %>% 
      dplyr::select(one_of(c("Record ID: 766-", "Event Name", "Ethnicity"))) %>%
      as.data.frame() %>% 
      rename_with(make.names) %>% 
      as.data.frame() , 
    by = c("Record.ID..766.", "Event.Name")) %>%
  mutate(diabetes_doctor = ifelse(dbc4_diabetes == "No", "2", "1"))

colnames(sglt2.samples.basic1)
table(sglt2.samples.basic1$dbc4_diabetes)
# dbc4_diabetes
# 
# No

# Diabetes
# yes no
# 1	Yes
# 0	No

table(sglt2.samples.basic1$diabetes_doctor)
# 1-Yes
# 2-No

sglt2.samples.basic1 %>% dplyr::filter(Record.ID..766. == "44") # NA value, need fix
table(sglt2.samples.basic1$Record.ID..766., sglt2.samples.basic1$Event.Name)
```

## basic file from redcap 2 --------------------------------------------------
```{r}
sglt2.samples.basic2 <- rio::import(paste0(Disk2, file.folder2, "/", basic.file2)) %>%
  dplyr::select(!one_of(c("Complete?", "Date:"))) %>%
  rename(dbc4_diabetes = Diabetes) %>%
  as.data.frame() %>%
  rename_with(make.names) %>% 
  mutate(Event.Name1 = stringr::str_split_fixed(Event.Name, " ", 2)[, 2] ) %>%
  mutate(Event.Name2 = stringr::str_split_fixed(Event.Name1, " ", 2)[, 1],
         Event.Name3 = ifelse(stringr::str_split_fixed(Event.Name1, " ", 2)[, 2] == "",  "",  ".1week")
  ) %>%
  mutate(patient_id =   paste0("766", stringr::str_pad( Record.ID..766., 2, pad = "0") ),
         # Event = readr::parse_number(as.character(Event.Name), na = c("Logs", "Checklists", "Unscheduled Visit", "Repeat Labs"))
  ) %>%
  # mutate_at(c('Event'), ~replace_na(., ""))  %>% 
  mutate(Event_id =  paste0("V", Event.Name2,  ifelse(Event.Name3 == "", "", Event.Name3) ) # paste0("V", stringr::str_pad(Event, 2, pad = "0") )
  ) %>%
  mutate(Event_id = replace(Event_id, Event_id == "V", "") ) %>%
  mutate(sample_id =  paste0(patient_id, ifelse(Event_id == "", "","_") , Event_id) )%>% 
  rename(Age = `Age..years.`,  # Age.at.Consent, 
         `Height_inches` =  Height..inches., 
         `Weight_pounds` =  Weight..pounds., 
         BMI = BMI, 
         Glucose = Glucose, 
         `A1c_Value`= A1c.Value)%>%  
  mutate(BMI = 703*Weight_pounds/(Height_inches^2)) %>%  
  mutate(
    Age_Group = ifelse(Age >= 60, "Older", ifelse(Age <60 & Age >= 45, "Middle", "Young")),
    # Gender = ifelse(Gender == "Female", "Female", "Male"),
    Prediabetes1 = ifelse(A1c_Value >= 5.7 & A1c_Value <= 6.4, "PreD", 
                          ifelse(A1c_Value > 6.4, "Diabetes","No" )),
    Prediabetes2 = ifelse(Glucose >= 100 & Glucose <= 125, "PreD", 
                          ifelse(Glucose > 125, "Diabetes", "No" )),
    Status = ifelse(BMI >= 30, "Obese",
                    ifelse(BMI >= 25 & BMI <30, "Overweight",
                           ifelse(BMI >= 18.5 & BMI <25, "Lean", "NA")))
  )%>%
  mutate(diabetes_doctor = ifelse(dbc4_diabetes == "No", "2", "1"))

intersect(colnames(sglt2.samples.basic1), colnames(sglt2.samples.basic2))


merge.cols = c("Event.Name1", "Event.Name2" ,"Event.Name3","patient_id", "Event_id" , "sample_id" , "Record.ID..766.", "Event.Name")
sglt2.samples <- sglt2.samples.basic1 %>%
  dplyr::select(-one_of(setdiff(intersect(colnames(sglt2.samples.basic1), colnames(sglt2.samples.basic2)) , merge.cols )) 
  )  %>% 
  full_join(sglt2.samples.basic2, 
            by = merge.cols)

sglt2.samples.basic2 %>% dplyr::filter(patient_id == "76644") # NA value, need fix
sglt2.samples.basic2 %>% dplyr::filter(Record.ID..766. == "44") # NA value, need fix
table(sglt2.samples.basic2$Record.ID..766., sglt2.samples.basic2$Event.Name)
```

## combine basic file from redcap 1 and basic file from redcap 2 -----------------------------------
```{r}
# change to numeric
num.cols = c("Fat..g.", "Region...Fat.", "Lean..g.", "Fat.Free..g.", "Albumin", "Bilirubin..Total",
             "TSH", "Urine.Glucose"    ,         "Urine.Protein"       ,      "Urine.Ketones"   ,        "Urine.Bilirubin",
             "Urine.Blood"     ,         "Urobilinogen"     ,        "Urine.Nitrite"     ,           "MoCA.Score" ,
             "Tissue..g." , "BMC..g."  ,"Albumin", "BMI"
)
for (num in num.cols) {
  sglt2.samples[[num]] <- as.numeric(sglt2.samples[[num]])
}

# combine based on each visit
sample_ids <- unique(sglt2.samples$sample_id)
cols = c('id',  'Event.Name_Orig', 'Event.Name', 'Visit..', 
         'Event.Name1', 'Event.Name2', 'Event.Name3', 'Event_id', 'sample_id')
sglt2 <- list()
for (ss in sample_ids) {
  # ss=sample_ids[1]
  sglt2[[stringr::str_split(ss, "_")[[1]][1]]][[ifelse(is.na(stringr::str_split(ss, "_")[[1]][2]), "Others", stringr::str_split(ss, "_")[[1]][2])]] <- sglt2.samples %>% dplyr::filter(sample_id == ss) %>% 
    mutate(
    across( where(is.character), ~ na_if(.x, "0")),
    across(where(is.numeric), ~ na_if(.x, 0)), # replace 0s contained in the columns with NA.
) %>% 
    dplyr::select_if(function(x) !(all(is.na(x)) | all(x==""))) %>% dplyr::select(!one_of(cols))
  # print(ss)
}
rm(cols, ss)

# combine based on Pre/Post
sglt2.combine <- list()
patient_ids <- unique(sglt2.samples$patient_id)
pre = c("V1", "V2", "V3", "V4", "V5", "V5.1week")
post = c("V6", "V7", "V8", "V9", "V10", "V11", "V12")
for (ss in names(sglt2)) {
  # ss=names(sglt2)[1]
  if( TRUE %in% (names(sglt2[[ss]]) %in% pre) ) {
    sglt2.combine[[ss]][["Pre"]] <- bind_rows(sglt2[[ss]][pre], .id = "Event")
  }
  if( TRUE %in% (names(sglt2[[ss]]) %in% post) ) {
    sglt2.combine[[ss]][["Post"]] <- bind_rows(sglt2[[ss]][post], .id = "Event")
  }
}
rm(pre, post, ss)

# combine based on Pre/Post
sglt2.combine2 <- list()
for (ss in names(sglt2.combine)) {
  tt.list <- sglt2.combine[[ss]] 
  if ( length(tt.list) > 1){
    for (pp in names(tt.list)) {
      tt <- sglt2.combine[[ss]][[pp]] 
      n = nrow(tt) + 1
      myNumCols <- which(unlist(lapply(tt, is.numeric)))
      myChaCols <- which(unlist(lapply(tt, is.character)))
      x1 <- colMeans(tt[, myNumCols], na.rm=TRUE)
      x2 <- apply(tt[, myChaCols], 2, function(x)unique(x[!is.na(x)]))
      tt[(n), myNumCols] <- x1
      tt[(n), myChaCols] <- x2
      sglt2.combine2[[ss]][[pp]]  <- tt[(n),]
    }
    print(ss)
  }
}
rm(ss, pp, tt, n, myNumCols, myChaCols, x1, x2 ,tt.list)

# combine Pre and Post
sglt2.combine3 <- list()
for (ss in names(sglt2.combine2)) {
  sglt2.combine3[[ss]] <- bind_rows(sglt2.combine2[[ss]], .id = "Pre_Post")
}

# combine all patients
sglt2.combine4 <- bind_rows(sglt2.combine3, .id = "patient_id2")
table(sglt2.combine4$Record.ID..766., sglt2.combine4$Pre_Post)
table(sglt2.combine4$Record.ID..766., sglt2.combine4$Group.Assignment.)
```


```{r}
# merge some basal information between pre and post
unique(sglt2.combine4[["Group.Assignment."]])
sglt2.combine4 <- sglt2.combine4 %>% dplyr::filter(!(patient_id == "76644")) # Remove NA group in "Group.Assignment.": 76644 is not assigned;
unique(sglt2.combine4[["Group.Assignment."]])

colnames(sglt2.combine4 %>% dplyr::filter(Pre_Post == "Pre") %>% dplyr::select_if(is.character))
cols = c("patient_id" , "Gender" ,"Race", "dbc4_diabetes", "Ethnicity","diabetes_doctor",
         "Group.Assignment." , "Age_Group"  , "Status" ,"Prediabetes1", "Prediabetes2" # , "Diabetes"  , "Group"
)   
basal <- sglt2.combine4 %>% dplyr::filter(Pre_Post == "Pre") %>% dplyr::select(one_of(cols))
unique(basal[["Group.Assignment."]])
# basal %>% dplyr::filter(patient_id == "76644") # NA value, need fix
sglt2.combine4 <- sglt2.combine4 %>% dplyr::select(!one_of(setdiff(cols, "patient_id"))) %>%
  left_join(basal, by = "patient_id")
unique(sglt2.combine4[["Group.Assignment."]])

# adding more colums
table(sglt2.combine4$dbc4_diabetes)
sglt2.prediabetes <- sglt2.combine4 %>% dplyr::filter(dbc4_diabetes == "No") %>% pull(patient_id)
sglt2.combine4 <- sglt2.combine4 %>%
  mutate(Diabetes = ifelse(patient_id %in% sglt2.prediabetes, "No", "Yes"))%>%  
  mutate(
    # Age_Group = ifelse(Age >= 60, "Older", ifelse(Age <60 & Age >= 45, "Middle", "Young")),
    # # Gender = ifelse(Gender == "Female", "Female", "Male"),
    # Prediabetes1 = ifelse(A1c_Value >= 5.7 & A1c_Value <= 6.4, "Pre", 
    #                       ifelse(A1c_Value > 6.4, "Diabetes","No" )),
    # Prediabetes2 = ifelse(Glucose >= 100 & Glucose <= 125, "Pre", 
    #                       ifelse(Glucose > 125, "Diabetes", "No" )),
    # Status = ifelse(BMI >= 30, "Obese",
    #                 ifelse(BMI >= 25 & BMI <30, "Overweight",
    #                        ifelse(BMI >= 18.5 & BMI <25, "Lean", "NA"))),
    Group = ifelse(`Group.Assignment.` == "Drug - dapagliflozin", "SGLT2i",
                   ifelse(`Group.Assignment.` == "Nutritional counseling", "NUT", NA)),
    sample_id = paste0(patient_id, "_", ifelse(Pre_Post == "Pre", "V5", "V11"))
  )



# # adjust and combine parameters between V1, V5, V11.
# sglt2.V1.cols <- c("id", "Record.ID..766.", "patient_id", "Event.Name" ,
#                    "Race","Gender",
#                    # "Age", "Age_Group",
#                    #"Height (inches)" , "Weight (pounds)",  "BMI", "Status",
#                    "Glucose" , "A1c_Value", "dbc4_diabetes")
# sglt2.sn.V1 <- sglt2.samples %>% dplyr::filter(`Event.Name` == "Visit 1") %>% arrange(id) %>% dplyr::select(all_of(sglt2.V1.cols)) %>% 
#   rename( id.V1 = id, `Event.Name_V1` = `Event.Name`
#   )
# 
# sglt2.V2.cols <- c("id", "Record.ID..766.", "patient_id", "Event.Name" ,
#                    "Age", "Age_Group"
# )
# sglt2.sn.V2 <- sglt2.samples %>% dplyr::filter(`Event.Name` == "Visit 2") %>% arrange(id) %>% dplyr::select(all_of(sglt2.V2.cols)) %>% 
#   rename( id.V2 = id, `Event.Name_V2` = `Event.Name`
#   )
# 
# sglt2.V5.cols <- c("id", "Record.ID..766.","patient_id", "Event.Name" ,
#                    "SingleNuclei", "Group.Assignment.", "Group",
#                    "Height_inches" , "Weight_pounds",  "BMI", "Status"
# )
# sglt2.sn.V5 <- sglt2.samples %>% dplyr::filter(`Event.Name` == "Visit 5") %>% arrange(id) %>% dplyr::select(all_of(sglt2.V5.cols)) # ,  SingleNuclei == "Yes"
# sglt2.sn.basal <- sglt2.sn.V5 %>% 
#   left_join(sglt2.sn.V1, by = c("Record.ID..766.", "patient_id")) %>% 
#   left_join(sglt2.sn.V2, by = c("Record.ID..766.", "patient_id"))
# 
# sglt2.V11.cols <- c("id", "Record.ID..766.","patient_id", "Event.Name" ,
#                     "SingleNuclei", 
#                     "Height_inches" , "Weight_pounds",  "BMI", "Status",
#                     "Glucose" , "A1c_Value")
# sglt2.sn.V11 <- sglt2.samples %>% dplyr::filter(`Event.Name` == "Visit 11") %>% arrange(id) %>% dplyr::select(all_of(sglt2.V11.cols)) # ,  SingleNuclei == "Yes"
# sglt2.sn.V11 <- sglt2.sn.V11 %>% 
#   left_join(sglt2.sn.V1 %>% dplyr::select(!all_of(c("Glucose" , "A1c_Value"))) , by = c("Record.ID..766.", "patient_id")) %>%
#   left_join(sglt2.sn.V2, by = c("Record.ID..766.", "patient_id")) %>%
#   left_join(sglt2.sn.V5 %>% dplyr::select(all_of(c("patient_id" , "Group.Assignment.", "Group"))), by = c("patient_id"))
# 
# # combine final
# sglt2.sn.all <- sglt2.sn.V11 %>% 
#   full_join(sglt2.sn.basal, by = intersect(colnames(sglt2.sn.V11),  colnames(sglt2.sn.basal)) ) %>% 
#   arrange(patient_id) # %>%
# # dplyr::select(!one_of(c("Group.Assignment.")))
# # sglt2.sn.all$BMI <- as.numeric(sglt2.sn.all$BMI)
# # sglt2.sn.all$dbc4_diabetes <- as.character(sglt2.sn.all$dbc4_diabetes)
# 
# sglt2.samples <- sglt2.samples %>%
#   dplyr::select(-one_of(setdiff(intersect(colnames(sglt2.samples), colnames(sglt2.sn.V11)) , "id" ))) %>% 
#   full_join(sglt2.sn.all, 
#             by = c("id") ) %>% 
#   arrange(patient_id)

colnames(sglt2.combine4)
# # sapply(sglt2.combine4, class)
table(sglt2.combine4$Age, sglt2.combine4$SingleNuclei)
table(sglt2.combine4$Age_Group, sglt2.combine4$SingleNuclei)
table(sglt2.combine4$Gender, sglt2.combine4$SingleNuclei)
table(sglt2.combine4$BMI)
sort(unique(sglt2.combine4$BMI))
table(sglt2.combine4$Status, sglt2.combine4$SingleNuclei)
table(sglt2.combine4$dbc4_diabetes)
table(sglt2.combine4$Diabetes, sglt2.combine4$SingleNuclei)
table(sglt2.combine4$Group.Assignment.)
table(sglt2.combine4$diabetes_doctor)
# 90 [ethnicity] Ethnicity radio
# 0 Hispanic or Latino
# 1 NOT Hispanic or Latino
# 2 Unknown / Not Reported
# 
# Custom alignment: LH
# 91 [race] Race dropdown
# 0 American Indian/Alaska Native
# 1 Asian
# 2 Native Hawaiian or Other Pacific Islander
# 3 Black or African American
# 4 White
# 5 More Than One Race
# 6 Unknown / Not Reported
# 92 [sex] Gender radio
# 0 Female
# 1 Male


sglt2.samples.final <- sglt2.combine4 
table(sglt2.samples.final[["Group"]], sglt2.samples.final[["Pre_Post"]])
unique(sglt2.samples.final[["Group"]])
sglt2.samples.final %>% filter( patient_id == "76644")
```

## compare sglt to STARR
```{r}
# "Blood.Pressure.Systolic" "systolic"
# "Blood.Pressure.Diastolic"   "diastolic" 
# "White.Blood.Cell...WBC"     "white_blood_cell"                    
# "Red.Blood.Cell...RBC"     "red_blood_cell"  
# "Hemoglobin"             "hemoglobin"                         
# "Hematocrit"              "hematocrit"                       
# "MCV"                      "mcv"                            
# "MCH"                      "mch"       
# "Platelets"            "platelets"          
# "Blood.Urea.Nitrogen..BUN."    "bun"  
# "Creatinine"                    "creatinine"                
#  "Sodium"                   "sodium"
# "Potassium"                     "potassium" 
# "Calcium"       "calcium"                                  
# "Protein..Total"        "protein_total"                         
# "Albumin"          "albumin"              
# "Alkaline.Phosphatase"      "alkaline_phosphatase"
# "Bilirubin..Total"           "total_bilirubin"                    
# "AST"                   "ast" 
# "ALT"                       "alt"                  
# "Cholesterol..Total"      "cholesterol"                       
# "Triglycerides"     "triglycerides"                               
# "HDL"           "hdl"
# "LDL"           "ldl"                                  
# "VLDL"          "vldl"                                 

# "MCHC"                                           "RDW"                                           
# "Chloride"                                      
#    "Manual.eGFR.calculation"                       
# "Monocyte"                                       "Granulocytes"                                   "Neutrophils"                                   
#  [61] "Eosinophils"                                    "Basophils"                                      
#  [73] "CO2"                                           
# [82] "TSH"                                            "Uric.Acid"                                      "Phosphorus"                                    
#  [85] "Date.of.lipids"                                 
#  [91] "PT"                                             "INR"                                            "PTT"                                           
#  [94] "Urine.pH"                                       "Urine.Glucose"                                  "Urine.Protein"                                 
#  [97] "Urine.Ketones"                                  "Urine.Bilirubin"                                "Urine.Blood"                                   
# [100] "Urobilinogen"                                   "Urine.Nitrite"                                  "MoCA.Score"   

```

## basic file 3 from sequencing: generate from counts excel file --------------------------------------------------
```{r}
# samples.basic3 <- rio::import(paste0(Disk3, file.folder3, "/", basic.file3)) %>%
#   dplyr::rename(Status.counts = Status)
# colnames(samples.basic3)
# intersect(colnames(sglt2.combine4), colnames(samples.basic3))
# 
# # merge files
# sglt2.samples.final <- sglt2.samples.final %>% 
#   full_join(samples.basic3 %>% 
#               dplyr::filter(Project == "SGLT2"), 
#             by = intersect(colnames(sglt2.combine4), colnames(samples.basic3)))
# colnames(STARR.samples)
```

## basic file 5 from lab: lab measurements --------------------------------------------------
```{r}
samples.basic5 <- rio::import(file = paste0(Disk5, file.folder5, "/", basic.file5)) # %>%
# rename(sample_id = id)
intersect(colnames(sglt2.samples.final), colnames(samples.basic5))
samples.basic5 %>% dplyr::filter(sample_id == "76639_V5") # one sample measured in two plate(Plate 1: STARR; Plate 2: SGLT2i)
table(samples.basic5$Plate)
samples.basic5 <- samples.basic5 %>% dplyr::filter(!(sample_id == "76639_V5" & Plate == "Plate 1"))
table(samples.basic5$Plate)
samples.basic5 %>% dplyr::filter(sample_id == "76639_V5")

# merge files
sglt2.samples.final <- sglt2.samples.final %>%
  left_join(samples.basic5,
            by = intersect(colnames(sglt2.samples.final), colnames(samples.basic5)))
colnames(sglt2.samples.final)
```



## combine all ------------------
```{r}
# final covert columns
# sglt2.samples.final$BMI <- as.numeric(sglt2.samples.final$BMI)
sglt2.samples.final$dbc4_diabetes <- as.character(sglt2.samples.final$dbc4_diabetes)
# sglt2.samples.final$Albumin <- as.numeric(sglt2.samples.final$Albumin)

# save
saveRDS(sglt2.samples.final, file = paste0(Disk2, file.folder2, "/",  "SGLT2.all.subject.info.rds"))
```


## sglt2_All single nuclei samples -------------------
```{r}
# df <- sglt2.samples.final %>% dplyr::filter( Agg == "Yes")
# table(df$SingleNuclei, df$Agg)
# table(df$Age_Group) 
# table(df$dbc4_diabetes)
# xlsx::write.xlsx(df, file = paste0(Disk2, file.folder2, "/", "SGLT2.sn.all.subject.info.xlsx"),
#                 # sheetName = "sglt2", row.names=FALSE)
# saveRDS(df, file = paste0(Disk2, file.folder2, "/", "SGLT2.sn.all.subject.info.rds"))
```

```{r}
rm(samples.basic3, sglt2.prediabetes, sglt2.samples.basic2, sglt2.samples.basic1, sglt2.sn.all, sglt2.sn.basal,
   sglt2.sn.V1, sglt2.sn.V11, sglt2.sn.V2, sglt2.sn.V5, sglt2.V1.cols, sglt2.V11.cols, sglt2.V2.cols, sglt2.V5.cols, df,
   num, num.cols, merge.cols)
```

```{r}
sessionInfo()
```

